### 2021-06-15 ANA-TOPQ-2019-17-PAPER-metadata.tex
updates on tau fakes and strategies

% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current $tHq$ interections of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
                   with 139 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}

>>>>

% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current $tHq$ ($q=u,c$) of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
                   in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector}

### 2021-06-15 sections/data_presel.tex
updates on tau fakes and strategies

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirement are defined targeting different signal decay mode:  
\begin{itemize}
	\item $t_h\lephad$: Targeting $t(q)H\to bqq(q)\lephad$ decay mode. Exactly one additional $\had$ with charge opposite to the lepton is further required. At least 3 jets with exactly one $b$-tagged are required.
	\item $t_l\hadhad$: Targeting $t(q)H\to bl\nu(q)\hadhad$ decay mode. At least two additional $\had$ with opposite charge are further required. At least 1 jet with exactly one $b$-tagged is required.
	\item $t_l\had$: Targeting $t(q)H\to bl\nu(q)\hadhad$ decay mode when one of the \had fails the tau reconstruction or identificaiton so that there is only one reconstructed \had candidate. Exactly one additional $\had$ with charge same for the lepton is further required. At least 2 jets with exactly one $b$-tagged are required.
\end{itemize}

The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ matched to the $\had$'s reconstructed by the trigger. No selected electrons or muons is required. The two \had candidates are required to have charges of opposite sign.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & \\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
\had  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($q$) & $q_\ell \times q_{\tau_{\mathrm{had,1}}} < 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ & $q_\ell \times q_{\tau_{\mathrm{had,1}}} > 0$ & $q_{\tau_{\mathrm{had,1}}} \times q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirement are defined targeting different signal decay mode:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\tau_l$ is required, including at least three jets with exactly one $b$-tagged jet.
\item $t_l\hadhad$: Targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-tagged jet.
\item $t_l\had$: Also targeting $t_lH$ and $t_lt(qH)$ with $H\to\hadhad$ decay when one of the \had fails the tau reconstruction or identificaiton so that there is only
  one \had candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-tagged jet.
\end{itemize}

The events in the hadronic channel are recorded by di-tau trigger, required to have both leading and trailing $\had$ passed the trigger.
The two \had candidates are required to have charges of opposite sign.

@@

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and trailing $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & \\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
\had  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  $\geq$ 3 jets & $\geq$1 jets & $\geq$2 jets & $\geq$3 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2021-06-15 sections/introduction.tex
updates on tau fakes and strategies

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted. Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels. More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.

>>>>

%The searches presented in this paper are focused on the dominant fermionic decay modes of the Higgs boson.
This paper is focused on the tau decay mode of the Higgs boson with the complete dataset collected during the Run~2 from 2016 to 2018. The corresponding integrated luminosity is 139.6 fb$^{-1}$. Both $\ttbar \to WbHq$ decay and $pp \to tH$ production are targeted and the signals are divided into several final states depending on the production modes and the
decay of $W$ boson hadronically and leptonically from the $t\rightarrow wb$ decay referred as $t_h$ and $t_l$. The $H\rightarrow \tau\tau$ decay detected to be in
either $\tlhad$ or $thadhad$ final states when the top decays hadronically ($t_h$) and only in $\thadhad$ when the top decay leptonically ($t_l$). 
Events with two hadronically decaying $\tau$-lepton candidate (\tauhad) without electron or muon are selected for hadronic channels. Events with at least one \tauhad with an additional electron or muon are selected from leptonic channels. More regions are exploited compared to the FCNC $\Htautau$ search conducted using partial Run~2 data.
The analysis also uses various $t\bar{t}$ control regions (CRtt) for calibration of tau fakes in Monte Carlo as well as
data-driven fake estimations from QCD multi-jet background.

### 2021-06-15 sections/signal_background_modeling.tex
updates on tau fakes and strategies

Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
is performed.} {\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo}) with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=1\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).

The nominal sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd} using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}.

@@

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one \had. Since the fake rate of \had candidate is much larger than electron or muon. So in the majority of the fake lepton events, the \had candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies. However the multi-jet background has large event rate and can contribute with both electron or muon and \had faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.  This kind of event is modelled by ABCD method widely used in ATLAS physics analyses.

@@

In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection requirements are analogous to those used to define the different SRs, except that the trailing $\had$ candidate is required to fail the medium $\had$ identification.

In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo. The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated control regions discussed in Section~\ref{sec:strategy_Htautau}.

>>>>

Samples of simulated $\ttbar \to WbHq$ events were generated with the next-to-leading-order (NLO) generator\footnote{In the following, 
the order of a generator should be understood as referring to the order in the strong coupling constant at which the matrix-element calculation 
is performed.} {\powheg}~v2 \cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
%{\amcatnlolong}~2.4.3~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO~\cite{Ball:2014uwa} parton distribution function (PDF) set and interfaced to {\pythia} 8.212~\cite{Sjostrand:2007gs} with the NNPDF2.3 LO~\cite{Ball:2012cx} PDF set for the modelling of parton showering, hadronisation, and the underlying event. 
The A14~\cite{ATLASUETune4} set of tuned parameters in {\pythia} controlling the description of multiparton interactions and  
initial- and final-state radiation, referred to as the tune, was used.
The signal sample is normalised to the same total cross section as used for the inclusive $t\bar{t}\to WbWb$ sample (see discussion below) and
assuming an arbitrary branching ratio of $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$.
The case of both top quarks decaying into $Hq$ is neglected in the analysis given the existing upper limits on $\BR(t \to Hq)$ (Section~\ref{sec:intro}).

The $tH$ signal events were generated by {\amcatnlolong}~2.6.2~\cite{Alwall:2014hca}  (referred to in the following as {\amcatnlo})
with the NNPDF3.0 NLO parton distribution function (PDF) set and interfaced to {\pythia} 8.212 with the NNPDF2.3 LO PDF set for the modelling of parton showering,
hadronisation, and the underlying event with the A14 tune.
Depending on either up quark or charm quark involved in the FCNC decay, the effective Lagrangian of $tqH$ interaction are parametrised using
dim-6 operators~\cite{fcnc_production_theory}. We obtain $\sigma(ug\to tH)$ = 1.4218 pb and $\sigma(cg\to tH)$ = 0.206 pb using $\BR_{\mathrm{ref}}(t\to Hq)=0.2\%$ as benchmark.

The nominal sample used to model the $\ttbar$ background was generated with the NLO generator {\powheg}~v2
%\cite{Frixione:2007nw,Nason:2004rx,Frixione:2007vw,Alioli:2010xd}
using the NNPDF3.0 NLO PDF set. The {\powheg} model parameter $h_{\textrm{damp}}$, which controls 
matrix element to parton shower matching and effectively regulates the high-$\pt$ radiation, was set to 1.5 times the top-quark mass. 
The parton showers, hadronisation, and underlying event were modelled by {\pythia}~8.210 with the NNPDF2.3 LO PDF set in combination with the A14 tune.
Alternative $\ttbar$ simulation samples used to derive systematic uncertainties are described in Section~\ref{sec:syst_bkgmodeling}. 
The generated $\ttbar$ samples are normalised to a theoretical cross section of $832^{+46}_{-51}$~pb, 
computed using \textsc{Top++}~v2.0~\cite{Czakon:2011xx} at next-to-next-to-leading order (NNLO), 
including resummation of next-to-next-to-leading logarithmic (NNLL) soft gluon 
terms~\cite{Cacciari:2011hy,Baernreuther:2012ws,Czakon:2012zr,Czakon:2012pz,Czakon:2013goa}.

@@

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than electron or muon. So in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is real, which is also proved by monte carlo studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, espcially to $t_l\had$ where the fake-lepton dominates and the jet multiplicity is low.  This kind of event is modelled by data-driven ABCD method by cutting on $\met$ and the lepton isolation, which is widely used in ATLAS physics analyses.

%\subsubsection{Fake $\tau$-lepton candidates}
%\label{sec:faketaus}
%The background with one or more fake $\had$ candidates mainly arises from $\ttbar$ or
%multijet production, depending on the search channel. 
%Studies based on the simulation show that, for all the above processes, fake $\had$ candidates primarily result from the 
%misidentification of light-quark jets, with the contribution from $b$-quarks and gluon jets playing a subdominant role.
%It is also found that the fake rate decreases for all jet flavours as the $\had$ candidate $\pt$ increases.

%In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$ candidates via loosened $\had$ requirements with% proper fake factors and partially from monte carlo. These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}. The CR selection %requirements are analogous to those used to define the different SRs, except that the trailing $\had$ candidate is required to fail the medium $\had$ identification.

%In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors derived from the dedicated $t\bar t$
%control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated control regions discussed in Section~\ref{sec:st%rategy_Htautau}.

@@

In the leptonic channels, the events with real electron or muon and fake taus are modelled by calibrated monte carlo with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:crsr},
aimed at fake taus from different origins. There are four kinds of fake taus that need to be calibrated: Type1) $\tau_{W}$'s with the opposite charge to the lepton;
Type2) $\tau_{W}$'s with the same charge as the lepton; Type 3) the fake taus from b-jets; Type4) the fake taus from other origins (mainly radiations).
These control regions are similar to the signal regions but with an additional b-jet or lepton defined as:
$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
Where di-lepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The regions of
$t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS are used to calibrate Type1 fake taus. Similarly for the Type2, the regions of $t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS are used.
A simultaneous fit to data is made to derive the scale factors for the fake taus, which consists of total 24 parameters including 3 $\pt$ bins (25-35, 35-45, 45-)GeV for 1 and 3
prong taus separately. The values of these scale factors range from 0.3 to 1.28 and are applied to the corresponding signal regions with single b-tagged jet.
In $t_l\thadhad$ channel, both taus can be fake, so the calibration is applied to each tau separately, following the same procedure as $\tlhad$ channels using the
lepton and fake tau charges, then the scale factors are multiplied together. The nominal value of the scale factors will vary along with other uncertainties from
combined preformace (CP) recommendations and theory uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

In the hadronic channels, this background is estimated partially from data by defining control regions (CR) enriched in fake $\had$
candidates via loosened $\had$ requirements with proper fake factors and partially from monte carlo.
These CRs do not overlap with the main search regions (SRs), discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define the different SRs, except
that the trailing $\had$ candidate is required to fail the medium $\had$ identification.
The events with fake trailing $\had$ candidate can be calculated by rescaling the templates of fake taus in the Fake-CR with proper fake factors (FF).
The templates are aquired by subtracting all MC background contributions with real sub-leading taus from data. The FFs are computed as
the ratio of the Data$-$MC$_\mathrm{real~tau}$ yields passing the medium tau ID to which failing the medium tau ID from different control regions and
the differences are treated as part of systematics.

### 2021-06-15 sections/strategy_Htautau.tex
updates on tau fakes and strategies

The $Wb(q)H\to q\bar{q}b(q)\tau\tau$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
In a significant fraction of the events, the lowest-$\pt$ jet from the $W$ boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in some decay mode signal events mixed with production mode having only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\had$ candidates, and on the number of light flavored jets:
($t_h\lephad$, 2j), ($t_h\lephad$, $\geq$4j), ($t_h\hadhad$, 3j), and ($t_h\hadhad$, $\geq$4j).

@@

The $Wb(q)H\to l\nu b(q)\tau\tau$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible. The variables calculated from the visible objects are directly used in the multivariate analysis.

>>>>

The $tt(qH)$ and $tH$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and the remaining $t\to Wb$ decay as well as an additional $q$-jet for $t\to qH$ decay. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
In a significant fraction of the events, the lowest-$\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in some decay mode signal events mixed with production mode having only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs depending on the number of leptons and
$\had$ candidates, and on the number of light flavored jets:
$t_l\hadhad$, $t_l\had$-1j, $t_l\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

\begin{table}
\centering
\caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & b-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

@@

In the  $t_lt(qH)$ and $t_lH$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible. The variables calculated from the visible objects are directly used in the multivariate analysis.
